My title

### 2024-11-23 paper/paper.qmd
update brm model section

>>>>

## Bayesian Model
After fitting the linear regression model using log and Box-Cox transformations, We extend the analysis by testing a Bayesian regression model (Model B). This model also predicts the log-transformed mean temperature (`log_mean_temp`) but incorporates prior and Bayesian inference to evaluate the uncertainty of parameter estimates. The predictors remain the same: wind speed (`wind_speed`), station pressure (`pressure_station`), Box-Cox-transformed total precipitation (`total_precipitation_boxcox`), and log-transformed gust speed (`log_gust_speed`).

The Bayesian model is defined as:

\begin{align}
\text{log\_mean\_temp} &\sim \mathcal{N}(\mu, \sigma^2), \\
\mu &= \beta_0 + \beta_1 \cdot \text{wind\_speed} + \beta_2 \cdot \text{pressure\_station} \\
&\quad + \beta_3 \cdot \text{total\_precipitation\_boxcox} + \beta_4 \cdot \text{log\_gust\_speed}.
\end{align}

The prior distributions for the parameters are:

- Coefficients ($\beta_1, \beta_2, \beta_3, \beta_4$): 
  $$
  \beta_i \sim \mathcal{N}(0, 10), \quad \text{for } i = 1, 2, 3, 4,
  $$

  reflecting moderate uncertainty centered around zero.

- Intercept ($\beta_0$): 
  $$
  \beta_0 \sim \mathcal{N}(0, 10),
  $$
  indicating prior uncertainty about the baseline log-mean temperature.

The model was fit using **Hamiltonian Monte Carlo (HMC)** via the `brms` package @brm. It uses:
- **4 chains** for convergence,
- **2000 iterations** per chain to ensure stability, 
- **4 cores** for parallel computation, enabling efficient sampling.
